Photo-D with LSST: stellar photometric distances out to the edge of the Galaxy

### 2024-01-26 paper/methodology.tex
Minor additions to the paper.

Figure~\ref{fig:cornerPlot3ex1} shows two-parameter covariances and marginal distributions for this case.
Note that true values are recovered within expected uncertainties, as well as non-vanishing covariances
between the parameters. The marginal distributions produced with the prior, likelihood and posterior maps,
shown in
% Figure~\ref{fig:margPost3D},   % FOR SOME REASON, THIS REFERENCE DOESN'T WORK
Figure 9,
illustrate the improvement in the ``knowledge'' of model
parameters between prior and posterior, brought by color measurements via the likelihood map.

>>>>

Figure~\ref{fig:cornerPlot3ex1} shows two-parameter covariances and marginal distributions for this case.
Note that true values are recovered within expected uncertainties, as well as non-vanishing covariances
between the parameters. The marginal distributions produced with the prior, likelihood and posterior maps,
shown in
% Figure~\ref{fig:margPost3D},   % FOR SOME REASON, THIS REFERENCE DOESN'T WORK
%Figure 9,
Figure~\ref{fig:margPost3D} illustrate the improvement in the ``knowledge'' of model
parameters between prior and posterior, brought by color measurements via the likelihood map.

### 2024-01-26 paper/paper.tex
first draft of Section 2
Minor additions to the paper.

\documentclass{aastex63} 
% \documentclass[12pt,preprint]{aastex}
% \documentclass[linenumbers, twocolumn, trackchanges]{aastex631}

@@

\author[0000-0000-0000-0000]{Tomislav Jurki\'{c}}
\affiliation{Faculty of Physics, University of Rijeka, Radmile Matej\v{c}i\'{c} 2, 51000 Rijeka, Croatia}

@@

\acknowledgements
\v{Z}.I. acknowledges funding by the Fulbright Foundation and thanks the Ru\d er Bo\v{s}kovi\'{c} Institute for hospitality.

@@

>>>>

\documentclass{aastex631} 
% \documentclass[12pt,preprint]{aastex}
% \documentclass[linenumbers, twocolumn, trackchanges]{aastex631}

@@

\author[0000-0002-4993-2939]{Tomislav Jurki\'{c}}
\affiliation{Faculty of Physics, University of Rijeka, Radmile Matej\v{c}i\'{c} 2, 51000 Rijeka, Croatia}

@@

\begin{acknowledgements}

This work is financed within the Tenure Track Pilot Programme of the Croatian Science Foundation and the Ecole Polytechnique Fédérale de Lausanne and the Project TTP-2018-07-1171 Mining the variable sky, with the funds of the Croatian-Swiss Research Programme.

\v{Z}.I. acknowledges funding by the Fulbright Foundation and thanks the Ru\dj er Bo\v{s}kovi\'{c} Institute for hospitality.

@@

\end{acknowledgements}
